Canopy leaf area of an evergreen Eucalyptus woodland does not respond to elevated

### 2015-05-01 manuscript.Rmd
added figure captions

>>>>

# Figure captions {.unnumbered}

Figure 1. (a) Target [CO2] (Ca) relative to the ambient Ca treatment at the EucFACE. The elevated Ca treatment proceeded in steps of 30 ppm, reaching +150 ppm in Feb. 2013. (b) Canopy transmittance ($\tau_d$) estimated from continuous time series of photosynthetically active radition (PAR) below and above the canopy, for highly diffuse conditions (Fdiff > 0.98) only. The solid lines are smoothed time series (with 95% confidence intervals) for each FACE ring (using a generalized additive model). Lines in blue colours denote ambient Ca treatment, red colours are elevated Ca (+150 ppm). Note steep increase in $\tau_d$ for Ring 6 around November 2014, due to an insect attack that resulted in near defoliation of the canopy. The arrow labelled ‘calibration’ indicates a drought period when τ_dsteadily increased, used to calibrate *L* estimates to cumulative litter production.

Figure 2. Average $L_\tau$ over the entire study period plotted against the basal area (sum of stem cross-sectional areas) of the FACE rings (R2 = 0.87, L = 0.909 + 0.0175 * BA). This relationship was used to calculate the L anomaly in Fig. 4, as the difference between L predicted from this regression and the actual $L_\tau$ at any given time.

Figure 3.Time series of L after correcting for plot-to-plot differences in basal area (BA). At every time point, the L anomaly was calculated as Lτ minus L fitted from the relationship with BA shown in Fig. 3. Each symbol is a value for a FACE ring, but the smooth curve (fitted with a generalized additive model) takes into account the random plot effect. Note that the 95% confidence always overlap, denoting no significant treatment effect at $\alpha$ = 0.05, except for a brief period in late 2014. This difference was due to an insect attack that led to partial defoliation of the canopy in one FACE ring (see Fig. 1).

Figure 4. Comparison of absolute changes in L ($\Delta L$) to litter production (in units of *L*), calculated for each litter collection period. To calculate ΔL, we fit a generalized additive model fitted to data from each FACE ring separately, and estimated the change in L during the litter collection period (and expressed as monthly changes, by accounting for the differences in actual lengths of litter collection periods). Green symbols indicate periods during which ΔL was positive (net leaf production), orange symbols when ΔL was negative (net leaf loss). Solid black lines are 1:1 lines, coloured lines regression lines with 95% confidence intervals. The strong positive correlation between litter production and ΔL during periods of net leaf production indicates that during leaf flushing, old leaves are actively shed.

Figure 5. Timeseries of litter production and estimated gross leaf production rate.

Figure 6.  (a) Total litter production for each of the FACE rings plotted against mean Lτ (p < 0.02). The ratio of mean L to annual litter production gives the mean leaf life span, shown in (b).  Leaf lifespan was not different between Ca treatments (p = 0.11).

Figure 7. Dynamics of L in relation to environmental drivers. (a) Smoothed time series of L estimated from τ_d, averaged across all six FACE rings. (b) From panel (a), we calculated the daily change in L (dL/dt), including the 95% confidence interval for the derivative of the time series. Green indicates significant positive dL/dt, red indicates significant negative dL/dt (at α=0.05). Four of the five significant positive increases corresponded to leaf flushing (arrows) observed in the field (except the third brief significant increase). (c) Soil water content estimated from over 0-80 cm soil depth interval, averaged across all sensors and all rings (blue line), and daily rainfall (black lines).  (d) Average daily air temperature with a fitted smoother.

Figure S1. Increase in gapfraction ($\tau_d$) and total litter production during the 2013 drought, calculated for each ring separately. Blue colours are $aC_a$, red colours eCa. (a) The change in τ_d and the 95% confidence interval was calculated from the slope of linear regression of τ_d with time (days since 8 July 2013)

Figure S2. Correlation between L estimated from diffuse canopy transmittance (τ_d) and from canopy photos. L from τ_d was calibrated to litter production during the 2013 drought (see Fig. 6?), but no further calibration was done for the comparison to canopy photos as shown here. Solid line is a 1:1 line, dashed line a regression line with a slope of 0.98 ± se (qirh , R2=0.71,P < 0.01), with the shading indicating the 95% confidence interval.

Figure S3. Comparison of τ_d  calculated from canopy transmittance during highly diffuse conditions (Fdiff > 0.98) only, or using all PAR data without filtering. Shown are daily average τ_d  for all six FACE rings (symbols), with a smoother (generalized additive model with 95% confidence intervals). Note the underestimation of τ_(d )during southern hemisphere winter, when solar angles are low, leading to higher attenuation of the direct beam, due to a longer path length through the canopy.
